# Setting up a Glossary

***
In this chapter, you learn how to:
  
- Setup and read csv files into R
- List terms and definitions by chapter
- List terms by the chapter in which they are first defined
- Use GitHub receive feedback and allow collaboration

***

A glossary can serve as a quick reference when the reader needs to recall a term’s definition or location within a book. This chapter can serve as a guide to setup a glossary in the `R Bookdown` environment. Please refer [here](https://bookdown.org/yihui/bookdown/get-started.html) for a refresher on `R Bookdown` if necessary.

## csv File Setup

The following include instructions on how to setup a csv file and read it into R.

1. Setup an excel file with 3 columns: Term, Definition, Chapter first defined.
2. We suggest using one excel file for all chapters for easy reference and sharing. However, you will have to save each chapter separately. Alternatively, you may use one excel file per chapter instead of having one central file then separating it.
3. Save the Excel file as a csv file.
4. Please note that if you make changes, do so in the Excel file not the csv file.

## Terms and Definitions by Chapter

This section describes how to create a list of important terms and their definitions listed according to the chapters in which they are found. 

We use an example from the glossary of Loss Data Analytics. First we display the list of terms and definitions for Chapter 1 of the book followed by the code used to generate it.

```{r setupGlossary, include=FALSE}
knitr::opts_chunk$set(comment = NA, echo = FALSE, message = FALSE)
```

### Chapter 1 Introduction to Loss Data Analytics

```{r}
library(pander)
chapter1 <- read.csv("~/R project/StyleGuideLDA/csv/Chapter1.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.1 <- cbind(chapter1[, 1], chapter1[, 2])
final.table1.1 <- as.data.frame(table1.1)
names(final.table1.1) <- c("Term", "Definition")
pander(final.table1.1)
```


Here is the code used for producing the list of terms and definitions:

```
### Chapter 1 Introduction to Loss Data Analytics

{r}
library(pander)
chapter1 <- read.csv("~/R project/StyleGuideLDA/csv/Chapter1.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
table1.1 <- cbind(chapter1[, 1], chapter1[, 2])
final.table1.1 <- as.data.frame(table1.1)
names(final.table1.1) <- c("Term", "Definition")
pander(final.table1.1)

```

## Terms and Chapter First Defined

This section describes how to create a list of terms by the chapter in which they are first defined. Certain terms are defined multiple times throughout the book, so this list can help the reader refer to the chapter in which a term is first used and defined. The terms listed here are sorted in alphabetical order.

We use an example from the glossary of Loss Data Analytics. Here, we use Chapter 1 and Chapter 2 of the book. We display the list of terms by chapter first defined then show the code used to generate it.

```{r results='hide'}
chapter2 <- read.csv("~/R project/StyleGuideLDA/csv/Chapter2.csv", header=TRUE,
                       na.strings=c("."), stringsAsFactors=FALSE)
```


```{r}
# Chapter 1
table2.1 <- cbind(chapter1[, 1], chapter1[, 3])

# Chapter 2
table2.2 <- cbind(chapter2[, 1], chapter2[, 3])

# Concatenate tables
table2 <- rbind(table2.1, table2.2)

# Sort alphabetically --> do not change
sort.table2 <- table2[order(table2[,1]), ] 

# Remove duplicates --> do not change
library(dplyr)
final.table2 <- as.data.frame(sort.table2)
names(final.table2) <- c("Term", "Chapter first defined")

# Generate table --> do not change
pander(distinct(final.table2, Term, .keep_all= TRUE))
```

Here is the code used for producing the list of terms by chapter first defined:

```
{r}
# Chapter 1
table2.1 <- cbind(chapter1[, 1], chapter1[, 3])

# Chapter 2
table2.2 <- cbind(chapter2[, 1], chapter2[, 3])

# Concatenate tables
table2 <- rbind(table2.1, table2.2)

# Sort alphabetically --> do not change
sort.table2 <- table2[order(table2[,1]), ] 

# Remove duplicates --> do not change
library(dplyr)
final.table2 <- as.data.frame(sort.table2)
names(final.table2) <- c("Term", "Chapter first defined")

# Generate table --> do not change
pander(distinct(final.table2, Term, .keep_all= TRUE))
```
Note that some lines of code say "do not change".  This is because theses lines of code apply to the final concatenated table which includes all the chapters. We need the concatenated table before we can sort all terms alphabetically and remove duplicates to generate the final table. 

## feedback and Collabpration

Creating GitHub for collaboration - refer to HappyGit

